\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Results for test case readability

\newcommand{\project}[1]{\textsc{#1}\xspace}
\newcommand{\Spoon}{\project{Spoon}}
\newcommand{\Guava}{\project{Guava}}
\newcommand{\Fastjson}{\project{Fastjson}}
\newcommand{\Seata}{\project{Seata}}
\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

@@

>>>>

\newcommand{\project}[1]{\textsc{#1}\xspace}
\newcommand{\Collections}{\project{Collections}}
\newcommand{\Threeten}{\project{Threeten}}
\newcommand{\Spatial}{\project{Spatial4j}}

@@

For the first time, the competition also assessed test case readability. To this,
a human study with 13 participants was conducted. A random class under test
was selected per the \Collections, \Threeten, and \Spatial projects, for which
every competing tool generated one test case. Then, each participant was asked
to rank these test cases on a scale from 1 (best) to 5 (worst), in terms of
readability. Overall, \EVOSUITE achieved the 2nd highest rank. The rank
distribution is shown in Figure~\ref{fig:readability}.

Most participants found \EVOSUITE-generated tests to be readable. When
\EVOSUITE ranked highest, they positively highlighted the thoroughness of
generated assertions, using edge cases as inputs, and the fact that tests
where short. When \EVOSUITE ranked lowest, participants critized the lack
of comments and descriptive test names, repetitiveness in the code, and
needless assertions.

\EVOSUITE's test case for \Collections was the longest among all presented
ones. Interestingly, it ranked both highest and lowest, with participants
stating that it was ``the most complete'' and the code being ``longer making
it more confusing''.

\begin{figure}
  \includegraphics[width=0.9\columnwidth]{./data/understandability}
  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
  \label{fig:readability}
\end{figure}
